Algebraic File Synchronization: Adequacy and Completeness

### 2016-12-01 p2/ordering.tex
Next step

In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, we will need the following results.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
We know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T'$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.

>>>>

In \cref{simple_reorder_equiv} we offer a formal proof that 
$\orderset{U}$ contains all possible permutations.
It is an important property of simple sequences: namely, that
all of their valid reorderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, we will need the following results.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
Let the first command in $S$ be $\cxynv$, that is, $S=\cxynv\cc S_0$.
We proceed by a nested induction on the number of commands before $\cxynv$ in $T$.
Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
Then from \cref{subseq_in_orderset} we know $T_1\in\orderset{S_0}$
and from the induction hypothesis $T_0\equiv S_0$ from which we get $T\equiv S$.

In our nested induction step we assume $T'\equiv S$ for all $T'\in\orderset{S}$
where there are at most $j$ commands in $T'$ to the left of $\cxynv$.
Let us then consider $T$ where there are $j+1$ such commands.
We aim to transform $T$ into $T''\equiv T$ by swapping $\cxynv$ with the preceding
command. Then from the induction hypothesis we will know $T\equiv T''\equiv S$,
which proves our lemma.

Let the command to the left of $\cxynv$ in $T$ be $\czwmv$.
If $n\unrel m$, then from \cref{ax_separate_commute} we know we can swap the two commands
and get an equivalent sequence.
Otherwise we note that necessarily $\cxynv$ and $\czwmv$ occur in the reverse order in $S$.
We know $n=\parent(m)$ or $m=\parent(n)$ cannot be the case,

TODO against definition

The only remaining case is when $n$ and $m$ are comparable but not in a parent--child relationship.

....................................

We know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T'$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.
